

\newcounter{countA}
\newtoggle{bisestile}
\togglefalse{bisestile}
\newcommand{\testbisestile}[1]{
	\setcounter{countA}{#1}
	\ifnumcomp{#1}{>}{1582}{
		\ifboolexpr{
			(test{ \ifnumcomp{(\value{countA}/4)*4-\value{countA}}{=}{0}}
			and not test {\ifnumcomp{(\value{countA}/100)*100-\value{countA}}{=}{0}})
			or test {\ifnumcomp{(\value{countA}/400)*400-\value{countA}}{=}{0}}
		}{\toggletrue{bisestile}}{\togglefalse{bisestile}}%gregoriano
	}
	{\ifnumcomp{(\value{countA}/4)*4-\value{countA}}{=}{0}
		{\toggletrue{bisestile}}{\togglefalse{bisestile}}%giuliano
	}
}

\newcounter{countS}
\newcounter{countT}
\newcounter{countM}
\newcommand{\stamparoman}[1]{\uppercase\expandafter{\romannumeral#1}}
\newcommand{\stampaanno}[1]{\setcounter{countS}{#1}\setcounter{countM}{-1}%
	\ifnumcomp{#1}{>}{0}{%
		\addtocounter{countS}{753}%
		Anno\ifbool{annodomini}{--\stamparoman{#1}--PCN}{}
		\ifbool{adurbe}{--\stamparoman{\thecountS}--AUC}{}}
	{\setcounter{countS}{\numexpr\thecountM*\thecountS}\setcounter{countT}{\thecountS}
		\setcounter{countS}{\numexpr 754-\thecountS}%
		Anno\ifbool{annodomini}{--\stamparoman{\thecountT}--ACN}{}
		\ifbool{adurbe}{--\stamparoman{\thecountS}--AUC}{}}}



\newcommand*{\latinoMensisDurata}[1]{%
	\ifcase#1
	\or
	31%
	\or
	28%
	\or
	31%
	\or
	30%
	\or
	31%
	\or
	30%
	\or
	31%
	\or
	31%
	\or
	30%
	\or
	31%
	\or
	30%
	\or
	31%
	\fi
}
\newcommand*{\latinoNonae}[1]{%
	\ifcase#1
	\or
	5%
	\or
	5%
	\or
	7%
	\or
	5%
	\or
	7%
	\or
	5%
	\or
	7%
	\or
	5%
	\or
	5%
	\or
	7%
	\or
	5%
	\or
	5%
	\fi
}

\newcommand*{\latinoPridieNonae}[1]{%
	\ifcase#1
	\or
	4%
	\or
	4%
	\or
	6%
	\or
	4%
	\or
	6%
	\or
	4%
	\or
	6%
	\or
	4%
	\or
	4%
	\or
	6%
	\or
	4%
	\or
	4%
	\fi
}

\newcommand*{\latinoIdus}[1]{%
	\ifcase#1
	\or
	13%Ianuarius%
	\or
	13%Februarius%
	\or
	15%Martius%
	\or
	13%Aprilis%
	\or
	15%Maius%
	\or
	13%Iunius%
	\or
	15%Iulius%
	\or
	13%Augustus%
	\or
	13%Septemper%
	\or
	15%October%
	\or
	13%November%
	\or
	13%December%
	\fi
}


\newcommand*{\latinoPridieIdus}[1]{%
	\ifcase#1
	\or
	12%Ianuarius%
	\or
	12%Februarius%
	\or
	14%Martius%
	\or
	12%Aprilis%
	\or
	14%Maius%
	\or
	12%Iunius%
	\or
	14%Iulius%
	\or
	12%Augustus%
	\or
	12%Septemper%
	\or
	14%October%
	\or
	12%November%
	\or
	12%December%
	\fi
}




\newcommand*{\latinoHora}[1]{%
	\ifcase#1
	tertia vigilia%
	\or
	tertia vigilia%
	\or
	tertia vigilia%
	\or
	tertia vigilia%
	\or
	quarta vigilia%
	\or
	quarta vigilia%
	\or
	quarta vigilia%
	\or
	hora prima%
	\or
	hora secunda%
	\or
	hora tertia%
	\or
	hora quarta%
	\or
	hora quinta%
	\or
	hora sexta%
	\or
	hora septima%
	\or
	hora octava%
	\or
	hora nona%
	\or
	hora decima%
	\or
	hora undecima%
	\or
	hora duodecima%
	\or
	prima vigilia%
	\or
	prima vigilia%
	\or
	secunda vigilia%
	\or
	secunda vigilia%
	\or
	secunda vigilia%
	\or
	secunda vigilia% 
	\fi
}

\newcommand{\latinoAnteDiemuno}[2]{%
	\latinoAnteDiem{\number\numexpr(\number\latinoNonae{#1}-\number#2+1)\relax}\space\latinoPridieNonaeNome{#1}}%
\newcommand{\latinoAnteDiemdue}[2]{%
	\latinoAnteDiem{\number\numexpr(\number\latinoIdus{#1}-\number#2+1)\relax}\space\latinoPridieIdusNome{#1}}%
\newcommand{\latinoAnteDiemtre}[2]{%
	\latinoAnteDiem{\number\numexpr(\number\latinoMensisDurata{#1}-\number#2+2)\relax}\space\latinoPridieKalendasNome{#1}}%
\newcommand{\latinoAnteDiemquattro}[1]{%
	\latinoAnteDiemBis{\number\numexpr(29-\number#1+2)\relax}}%
\newcommand{\latinoMensisPridie}{\ifbool{compatta}{Pr.\space}{Pridie\space}}

\newcommand*{\latinoPridieKalendasNome}[1]{%
	\ifbool{compatta}{%%
		\ifcase#1%
		\or
		Kal.~Feb.%
		\or
		Kal.~Mart.%
		\or
		Kal.~Apr.%
		\or
		Kal.~Mai.%
		\or
		Kal.~Iun.%
		\or
		Kal.~Quint.%
		\or
		Kal.~Sext.%
		\or
		Kal.~Sept.%
		\or
		Kal.~Oct.%
		\or
		Kal.~Nou.%
		\or
		Kal.~Sec.%
		\or
		Kal.~Ian.%
		\fi}{%
	\ifcase#1%%
	\or
	Kalendas Februarias%
	\or
	Kalendas Martias%
	\or
	Kalendas Apriles%
	\or
	Kalendas Maias%
	\or
	Kalendas Iunias%
	\or
	Kalendas Quintiles%
	\or
	Kalendas Sextiles%
	\or
	Kalendas Septembres%
	\or
	Kalendas Octobres
	\or
	Kalendas Nouembres%
	\or
	Kalendas Decembres%
	\or
	Kalendas Ianuarias%
	\fi}}%
\newcommand*{\latinoKalendis}[1]{%
		\ifbool{compatta}{%
					\ifcase#1%
					\or
					Kal.~Feb.%
					\or
					Kal.~Mart.%
					\or
					Kal.~Apr.%
					\or
					Kal.~Mai.%
					\or
					Kal.~Iun.%
					\or
					Kal.~Quint.%
					\or
					Kal.~Sext.%
					\or
					Kal.~Sept.%
					\or
					Kal.~Oct.%
					\or
					Kal.~Nou.%
					\or
					Kal. Sec.%
					\or
					Kal. Ian.%
					\fi}{%
	\ifcase#1%
	\or
	Kalendis Ianuariis%
	\or
	Kalendis Februariis%
	\or
	Kalendis Martiis%
	\or
	Kalendis Aprilibus%
	\or
	Kalendis Maiis%
	\or
	Kalendis Iuniis%
	\or
	Kalendis Quintilibus%
	\or
	Kalendis Sextilibus%
	\or
	Kalendis Septembribus%
	\or
	Kalendis Octobribus%
	\or
	Kalendis Nouembribus%
	\or
	Kalendis Decembribus%
	\fi}}%
\newcommand*{\latinoNonaeNome}[1]{%
	\ifbool{compatta}{%
		\ifcase#1%
		\or
		Non. Ian.%
		\or
		Non. Feb.%
		\or
		Non. Mart.%
		\or
		Non. Apr.%
		\or
		Non. Mai.%
		\or
		Non. Iun.%
		\or
		Non. Quint.%
		\or
		Non. Sext.%
		\or
		Non. Sept.%
		\or
		Non. Oct.%
		\or
		Non. Nou.%
		\or
		Non. Dec.%
		\fi}{%
	\ifcase#1%
	\or
	Nonis Ianuariis%
	\or
	Nonis Februariis%
	\or
	Nonis Martiis%
	\or
	Nonis Aprilibus%
	\or
	Nonis Maiis%
	\or
	Nonis Iuniis%
	\or
	Nonis Quintilibus%
	\or
	Nonis Sextilibus%
	\or
	Nonis Septembribus%
	\or
	Nonis Octobribus%
	\or
	Nonis Nouembribus%
	\or
	Nonis Decembribus%
	\fi}}%
\newcommand*{\latinoPridieNonaeNome}[1]{%
	\ifbool{compatta}{%	
		\ifcase#1%
		\or
		Non. Ian.%
		\or
		Non. Feb.%
		\or
		Non. Mart.%
		\or
		Non. Apr.%
		\or
		Non. Mai.%
		\or
		Non. Iun.%
		\or
		Non. Quint.%
		\or
		Non. Sext.%
		\or
		Non. Sept.%
		\or
		Non. Oct.%
		\or
		Non. Nou.%
		\or
		Non. Dec.%
		\fi}{%
		\ifcase#1%
		\or
		Nonas Ianuarias%
		\or
		Nonas Februarias%
		\or
		Nonas Martias%
		\or
		Nonas Apriles%
		\or
		Nonas Maias%
		\or
		Nonas Iunias%
		\or
		Nonas Quintiles%
		\or
		Nonas Sextiles%
		\or
		Nonas Septembres%
		\or
		Nonas Octobres%
		\or
		Nonas Nouembres%
		\or
		Nonas Decembres%
		\fi}}%

\newcommand*{\latinoIdusNome}[1]{%
\ifbool{compatta}{%
	\ifcase#1%
	\or
	Id. Ian.%
	\or
	Id. Feb.%
	\or
	Id. Mart.%
	\or
	Id. Apr.%
	\or
	Id. Mai.%
	\or
	Id. Iun.%
	\or
	Id. Quint.%
	\or
	Id. Sext.%
	\or
	Id. Sept%
	\or
	Id. Oct.%
	\or
	Id. Nou.%
	\or
	Id. Dec.%
	\fi}{%
	\ifcase#1%
	\or
	Idibus Ianuariis%
	\or
	Idibus Februariis%
	\or
	Idibus Martiis%
	\or
	Idibus Aprilibus%
	\or
	Idibus Maiis%
	\or
	Idibus Iuniis%
	\or
	Idibus Quintilibus%
	\or
	Idibus Sextilibus%
	\or
	Idibus Septembribus%
	\or
	Idibus Octobribus%
	\or
	Idibus Nouembribus%
	\or
	Idibus Decembribus%
	\fi}}%
\newcommand*{\latinoPridieIdusNome}[1]{%
\ifbool{compatta}{%
		\ifcase#1%
		\or
		Id. Ian.%
		\or
		Id. Feb.%
		\or
		Id. Mart.%
		\or
		Id. Apr.%
		\or
		Id. Mai.%
		\or
		Id. Iun.%
		\or
		Id. Quint.%
		\or
		Id. Sext.%
		\or
		Id. Sept%
		\or
		Id. Oct.%
		\or
		Id. Nou.%
		\or
		Id. Dec.%
		\fi}{%
	\ifcase#1%
	\or
	Idus Ianuarias%
	\or
	Idus Februarias%
	\or
	Idus Martias%
	\or
	Idus Apriles
	\or 
	Idus Maias%
	\or
	Idus Iunias%
	\or
	Idus Quintiles%
	\or
	Idus Sextiles%
	\or
	Idus Septembres%
	\or
	Idus Octobres%
	\or
	Idus Nouembres%
	\or
	Idus Decembres
	\fi}}%
\newcommand*{\latinoAnteDiem}[1]{%
	\ifbool{compatta}{%
			\ifcase#1%
			\or
			1%
			\or
			2%
			\or
			A.~d.~III%
			\or
			A.~d.~IV%
			\or
			A.~d.~V%
			\or
			A.~d.~VI%
			\or
			A.~d.~VII%
			\or
			A.~d.~VIII%
			\or
			A.~d.~IX%
			\or
			A.~d.~X%
			\or
			A.~d.~XI%
			\or
			A.~d.~XII%
			\or
			A.~d.~XIII%
			\or
			A.~d.~XIV%
			\or
			A.~d.~XV%
			\or
			A.~d.~XVI%
			\or
			A.~d.~XVII%
			\or
			A.~d.~XVIII%
			\or
			A.~d.~XIX%
			\fi}{%
	\ifcase#1%
	\or
	1%
	\or
	2%
	\or
	Ante diem tertium%
	\or
	Ante diem quartum%
	\or
	Ante diem quintum%
	\or
	Ante diem sextum%
	\or
	Ante diem septimum%
	\or
	Ante diem octavum%
	\or
	Ante diem nonum%
	\or
	Ante diem decimum%
	\or
	Ante diem undecimum%
	\or
	Ante diem duodecimum%
	\or
	Ante diem tertium decimum%
	\or
	Ante diem quartum decimum%
	\or
	Ante diem quintum decimum%
	\or
	Ante diem sextum decimum%
	\or
	Ante diem septimum decimum%
	\or
	Ante diem duodevicesimum%
	\or
	Ante diem undevicesimum%
	\fi}}%
\newcommand*{\latinoAnteDiemBis}[1]{%
	\ifbool{compatta}{%
			\ifcase#1%
			\or
			1%
			\or
			2%
			\or
			A.~d.~III Kal.~Mart.%
			\or
			A.~d.~IV Kal.~Mart.%
			\or
			A.~d.~V Kal.~Mart.%
			\or
			A.~d.~bis~VI Kal.~Mart.%
			\or
			A.~d.~VI Kal.~Mart.%
			\or
			A.~d.~VII Kal.~Mart.%
			\or
			A.~d.~VIII Kal.~Mart.%
			\or
			A.~d.~IX Kal.~Mart.%
			\or
			A.~d.~X Kal.~Mart.%
			\or
			A.~d.~XI Kal.~Mart.%
			\or
			A.~d.~XII Kal.~Mart.%
			\or
			A.~d.~XIII Kal.~Mart.%
			\or
			A.~d.~XIV Kal.~Mart.%
			\or
			A.~d.~XV decimum Kal.~Mart.%
			\or
			A.~d.~XVI Kal.~Mart.%
			\or
			A.~d.~XVII Kal.~Mart.%
			\or
			A.~d.~XVIII Kal.~Mart.%
			\or
			A.~d.~XIX Kal.~Mart.%
			\fi}{%
	\ifcase#1%
	\or
	1%
	\or
	2%
	\or
	Ante diem tertium Kalendas Martias%
	\or
	Ante diem quartum Kalendas Martias%
	\or
	Ante diem quintum Kalendas Martias%
	\or
	Ante diem bis sextum Kalendas Martias%
	\or
	Ante diem sextum Kalendas Martias%
	\or
	Ante diem septimum Kalendas Martias%
	\or
	Ante diem octavum Kalendas Martias%
	\or
	Ante diem nonum Kalendas Martias%
	\or
	Ante diem decimum Kalendas Martias%
	\or
	Ante diem undecimum Kalendas Martias%
	\or
	Ante diem duodecimum Kalendas Martias%
	\or
	Ante diem tertium decimum Kalendas Martias%
	\or
	Ante diem quartum decimum Kalendas Martias%
	\or
	Ante diem quintum decimum Kalendas Martias%
	\or
	Ante diem sextum decimum Kalendas Martias%
	\or
	Ante diem septimum decimum Kalendas Martias%
	\or
	Ante diem duodevicesimum Kalendas Martias%
	\or
	Ante diem undevicesimum Kalendas Martias%
	\fi}}%